---
title: "Homework 6"
format: pdf
authors: "Febe Lin, Ramtin Ranjpour, & James Phillips"
editor: visual
bibliography: hw6-references.bib
link-citations: true
execute:
  eval: true
  echo: false
  warning: false
  fig-width: 6.5
  fig-height: 8
---

# 

```{r}
#| include: false
library(here)
library(tidyverse)
library(rio)
```

```{r}
star <- import(here("data/star.csv"))
```

The authors of this homework would like to thank @R, @here, @tidyverse, and @rio for their technological contributions. Though this specific publication did not directly contribute, we would like to thank its authors [@nese2017two] for their moral support and guidance.

\newpage

```{r, fig.width=5, fig.height=7}

ggplot(star, aes(x = totexp, y = tmathss)) +
  geom_point(color = "grey60", alpha = 0.3, size = 0.3) +
  geom_smooth(aes(color = frl), method = "lm", se = TRUE, size = 1.1, alpha = 0.2) +
  scale_color_discrete(
    name = "Lunch status",
    labels = c("Paid Meals", "Free/Reduced Price Meals")
  ) +
  labs(
    x = "Teacher Experience (years)",
    y = "Total Math Scale Score",
    title = "Relation between teacher experience and math scores",
    subtitle = "Separate regression lines displayed by free/reduced price lunch status"
  ) +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom")


```

# Discussion

The scatterplot with fitted regression lines shows a positive relationship between teacher experience and students\' math achievement. Students taught by more experienced teachers score higher. Additionally, students who pay for lunch consistently score higher than those receiving free/reduced-price lunch across all levels of teacher experience.

# References

# 
